# Libraries

```{r}
#| include: false
library(sf)
library(tmap)
library(tidyverse)
library(here)
library(units)
library(knitr)
```

# Source Functions

```{r}
#| include: false
source(knitr::purl(here("R",'development', "separate_functions.qmd")))
```

# Input Data

```{r}
#| include: false



#limit_lu <- st_read('/capstone/pyforest/data/Permited_Land_Use/limite_put.shp')



#|>  st_make_valid()|> st_transform("EPSG:32721")

# riverline <- st_read('/capstone/pyforest/data/river_05242.shp')) |>
#   st_make_valid() |>
#   st_transform("EPSG:32721")

limit_lu <- st_read('/Users/romero61/../../capstone/pyforest/data/mock_properties/mock_properties.shp') |>
  head(n = 1)

hydro <- st_read('/Users/romero61/../../capstone/pyforest/data/river_buffer/rivers.shp')
#hydro <- st_read(here('/capstone/pyforest/data/roads_hydrology/ly_hid2.shp'))  


#|> st_make_valid() |> st_transform("EPSG:32721")


#prop_limit <- st_read(here('/capstone/pyforest/Sample Data/catastro_forestal_3ej.shp')) 


#%>%  st_make_valid() |>  st_transform("EPSG:32721")
# prop_limit_05242 <- prop_limit %>% 
#   filter(cat == "05242")
```


# Select Property

```{r}

property_boundary <- select_property(3)
plot(property_boundary)

```

# Riparian Corridor check 

```{r}
if (lengths(st_intersects(property_boundary, hydro)) > 0) {
      riparian <- st_intersection(hydro, property_boundary) |>
        st_make_valid() }
plot(riparian)
```


```{r}
# |include: false
riparian_corridor <- riparian_buffer()
plot(riparian_corridor)
```



```{r}
y <- sqrt(999999 / (1/3)) + (50)

x <- sqrt((999999 * (1/3))) + (50)
```




# Input of Paddock and Hedgerow Dimensions

```{r}
pad_hedg_dim <- property_dimensions(desired_area = 999999 ,
                                hedgerow_width = 100,
                                width_paddock = 4,
                                height_paddock = 3)

```

# Create Grid & Rotate

```{r}
property_grid <- grid_rotate()
plot(property_grid)
st_area(property_grid)
```

```{r}
# cut grid with river
property_fragment <- riparian_cut()
tmap_mode('view')
#tmap_options(check.and.fix = TRUE)
tm_shape(property_grid) +
  tm_sf(col = 'forestgreen') +
tm_shape(riparian_corridor) +
  tm_borders(col = 'red') +
  tm_shape(property_fragment) +
  tm_sf(col = 'beige')
plot(property_fragment)
```

```{r}
#build if statement where n has to be irregular after start collecting by number
#
#

test_boundary_sf <- st_as_sf(property_grid)
  
  test_areas <- test_boundary_sf |>
    mutate(cell_area = st_area(test_boundary_sf),
           cell_number = 1:nrow(test_areas))
  max_area <- max(test_areas$cell_area)
   
   test_areas2 <- test_areas |>
    mutate(cell_number = 1:nrow(test_areas))
   

tm_shape(test_areas) +
  tm_sf(col = 'cell_area')   
      

```
```{r}
tm_shape(test_areas2) +
  tm_sf(col = 'cell_number')
```

```{r}
tm_shape(orest) +
  tm_sf()
```


```{r}


n <- 1
  repeat {
    tf <-  test_areas %>%
      arrange(test_areas$cell_area) %>%
      head(n)
    
    
    check <-
      sum((st_area(tf) / sum(st_area(test_areas))) * 100 )
    
    if (check >= set_units(25,1) ) {
      break}
    n <- n + 1
  }
```


```{r}

test_boundary_sf <- st_as_sf(property_grid)
  
  test_areas <- test_boundary_sf |>
    mutate(cell_area = st_area(test_boundary_sf),
           cell_number = 1:nrow(test_areas))
  max_area <- max(test_areas$cell_area)
  

n <- 1
repeat {
  tf <- test_areas %>%
    arrange(cell_area) %>%
    head(n)
  
  check <- sum((st_area(tf) / sum(st_area(test_areas))) * 100)
  
  if (check >= set_units(25, 1)) {
    last_row <- tf |> slice_tail()
    if(last_row$cell_area == max_area) {
          repeat{  n <- n - 1}

      tf2 <- test_areas %>%
        filter(cell_area == max(test_areas$cell_area)) %>%
        arrange(cell_number) %>%
        head(n)
      final_tf <- bind_rows(tf, tf2)
      check <- sum((st_area(final_tf) / sum(st_area(test_areas))) * 100)}
    }
    break
  }
  n <- n + 1
}

```



# Create Forest Reserve ≥ 25% & \< 28%


```{r}
 rid_boundary_sf <- st_as_sf(property_grid)
  
  ell_areas <- rid_boundary_sf |>
    mutate(cell_area = st_area(rid_boundary_sf))
  
  n <- 1
  repeat {
    orest <-  ell_areas %>%
      arrange(cell_area) %>%
      head(n)
    rea_check <-
      sum((st_area(orest) / sum(st_area(ell_areas))) * 100 )
    
    if (rea_check >= set_units(25,1) ) {
      break
    }
    n <- n + 1
  }
plot(orest)
```


```{r}
forest_reserve <- reserve()
  tm_shape(forest_reserve) +
  tm_sf(col = 'blue')

st_area(forest_reserve)
plot(forest_reserve)
```

# Property w/o reserve area

```{r}
grd_sf <- st_as_sf(property_fragment)
  fr_sf <- st_as_sf(forest_reserve)
  property_remaining <- st_difference(property_fragment,forest_reserve ) 

# st_write(property_remaining, "/Users/romero61/../../capstone/pyforest/data/simulation_test/prop_remaining.shp")
plot(property_remaining)
```


```{r}
property_remaining <- no_reserve_area()
plot(property_remaining)
st_area(property_remaining)
```

# Hedgerows

```{r}
# Workshop function


rop_combine <- property_remaining |> st_make_valid() |> st_simplify() |> st_union(is_coverage = TRUE)
  plot(rop_combine)
  rop_combine
  # Filter out POINT and GEOMETRYCOLLECTION geometries

  egrid <- grid_rotate(rop_combine)
  


# Filter out POINT geometries
egrid2 <- property_remaining[!st_geometry_type(property_remaining) %in% c("POINT")]
 

# # Extract point geometries from grid
# point_geoms <- lapply(st_geometry(egrid), function(geom) {
#   if(st_geometry_type(geom) == "POINT") {
#     st_geometry(geom)
#   } else if(st_geometry_type(geom) == "GEOMETRYCOLLECTION") {
#     st_collection_extract(geom, "POINT")
#   } else {
#     NULL
#   }
# })
# 
# # Combine all point geometries into a single object
# point_geoms <- do.call(rbind, point_geoms)
# # Extract LINESTRING and POLYGON geometries from GEOMETRYCOLLECTION objects
# gc_geoms <- lapply(st_geometry(egrid2), function(geom) {
#   if(st_geometry_type(geom) == "GEOMETRYCOLLECTION") {
#     st_collection_extract(geom, c("LINESTRING", "POLYGON"))
#   } else {
#     st_geometry(geom)
#   }
# })
# 
# # Combine all geometries into a single object
# gc_geoms <- do.call(rbind, gc_geoms)
# 
# # Combine LINESTRING, POLYGON, and point geometries into a single object
# egrid3 <- st_sfc(gc_geoms, point_geoms)

# Cast combined geometries to MULTILINESTRING
egrid3 <- st_cast(egrid2, to = "MULTILINESTRING")

# Make sure resulting geometries are valid
egrid3 <- st_make_valid(egrid3)
  
tmap_options(check.and.fix = TRUE)

  edge <- st_buffer(egrid3, dist = 50)  |>  st_as_sf() |> st_make_valid()  |>  st_union() 
tm_shape(edge) +
  tm_sf()

```

```{r}
hedgerows <- make_hedges()
#Cut off buffer that extends over property boundary
hedge <- st_erase(hedgerows,property_boundary) 
hedges <- st_difference(hedgerows, hedge)
cut_reserve <- st_intersection(forest_reserve,hedges  )
hedges <- st_difference(hedges, cut_reserve)
  
plot(hedges)
plot(cut_reserve, col = 'green')

```

# Paddocks

```{r}
paddocks <- make_paddocks()
plot(paddocks, col = 'beige')
st_area(paddocks)
```

# If there is a corridor cut edges

```{r}
if(is.null(riparian_corridor) == FALSE) {
  riparian_area <- round(st_area(riparian_corridor),2)
  riparian_area_per <-
    (st_area(riparian_corridor) / st_area(property_boundary)) * 100
  final_hedgerow <- st_difference(hedges, riparian_corridor)
  
} else{
  riparian_area <- NA
  riparian_area_per <- NA
  final_hedgerow <- hedges
}
 plot(final_hedgerow)
```

# Layers

```{r}

tmap_mode('plot')
tm_shape(property_boundary) +
  tm_sf('red') +
tm_shape(forest_reserve) +
  tm_polygons(col = 'forestgreen')+
tm_shape(final_hedgerow) +
  tm_polygons(col = 'green')+
tm_shape(paddocks) +
  tm_sf('beige')+
  tm_shape(riparian_corridor) +
  tm_polygons(col = 'lightcyan')
#tmap_save(fr35,'/capstone/pyforest/capstone/R/undeveloped_region_simulation/fr35.png')





tm_shape(paddocks) +
  tm_sf('beige')
  
tm_shape(final_hedgerow) +
  tm_polygons(col = 'green')  
  
tm_shape(forest_reserve) +
  tm_polygons(col = 'forestgreen')
  
tm_shape(riparian_corridor) +
  tm_polygons(col = 'lightcyan')

tm_shape(property_boundary) +
  tm_sf()

```

# Final Areas

```{r}
statistics <- tibble(
  id = property_boundary$cat,
  property_area = st_area(property_boundary) |> drop_units(),
  property_units = 'm^2',
  fr_area = st_area(forest_reserve) |> drop_units(),
  fr_units = 'm^2',
  fr_per = round((st_area(forest_reserve) / st_area(property_boundary)) * 100,2) |> drop_units()
,
  paddocks_area = round(sum(st_area(paddocks)),2) |> drop_units(),
  paddocks_units = 'm^2',
  paddocks_per = round(sum(st_area(paddocks)) / st_area(property_boundary)* 100 ,2) |>  drop_units(),
  hedgerow_area = st_area(final_hedgerow) |>  drop_units(),
  hedgerow_units = 'm^2',
  hedgerow_per = round((sum(st_area(final_hedgerow)) / st_area(property_boundary)) * 100,2) |> drop_units(),
  riparian_area = riparian_area |> drop_units(),
  riparian_units = 'm^2',
  riparian_per = riparian_area_per |> drop_units()
    )
c(statistics) 
#saveRDS(statistics, "statistics.rds")
```

```{r}

st_area(paddocks)
c(statistics |> mutate(total_area = sum(fr_per, paddocks_per,hedgerow_per, riparian_per) ))
```
