```{r}
library(sf)
library(tidyverse)
library(here)
library(units)
library(knitr)
library(tictoc)
library(flextable)
library(parallel)
library(purrr)
library(foreach)
library(doParallel)
library(furrr)
library(beepr)
library(gt)
```



```{r}
#source(knitr::purl(here("src", "boundary_registry_data.qmd")))
source(knitr::purl(here('src', "lup_simulator.qmd")))

```


```{r}
limit_lu <- st_read('/Users/romero61/../../capstone/pyforest/data/mock_properties/mock_properties.shp')

#to read in rework if not loaded
# limit_lu <- st_read("/Users/romero61/../../capstone/pyforest/data/rework/rwk_over28.gpkg")

hydro <- st_read('/Users/romero61/../../capstone/pyforest/data/river_buffer/river_buffer.gpkg')

```

# Parallel Functions

```{r}
# create a vector of unique combinations of width_paddock # Function to create unique combinations of width_paddock and height_paddock
create_paddock_dims <- function() {
  expand_grid(width_paddock = 1:4, height_paddock = 1:4) %>%
    subset(width_paddock != height_paddock | width_paddock == 1)
}
```


```{r}
generate_statistics <-
  function(property_boundary,
           width_paddock,
           height_paddock,
           forest_reserve,
           paddocks,
           final_hedgerow,
           riparian_area,
           riparian_area_per) {
     # print("Inside generate_statistics")
    # 
    # print("Checking property_boundary")
    # print(property_boundary)
    # print("Checking forest_reserve")
    # print(forest_reserve)
    # print("Checking paddocks")
    # print(paddocks)
    # print("Checking final_hedgerow")
    # print(final_hedgerow)
    # print('Checking property')
    # print(property_boundary$cat)
    # print("Checking riparians")
    # print(riparian_area)
    # print(riparian_area_per)

    statistics <- tibble(
      cat = property_boundary$cat,
      ratio_xy = paste(width_paddock, "/", height_paddock),
      property_area = st_area(property_boundary) |> drop_units(),
      property_units = "m^2",
      
      fr_area = sum(st_area(forest_reserve)) |> drop_units(),
      fr_units = "m^2",
      fr_per = round((sum((st_area(forest_reserve)) / st_area(property_boundary))) * 100,2) |> drop_units(),
      
      paddocks_area = round(sum(st_area(paddocks)),2) |> drop_units(),
      paddocks_units = "m^2",
      paddocks_per = round(sum(st_area(paddocks)) / st_area(property_boundary)* 100 ,2) |>  drop_units(),
      
      hedgerow_area = ifelse(is.null(final_hedgerow), NA, st_area(final_hedgerow)),
      hedgerow_per =  round((sum(st_area(final_hedgerow)) / st_area(property_boundary)) * 100,2) |> drop_units(),
      
      riparian_area = riparian_area ,
      riparian_units = 'm^2',
      riparian_per = riparian_area_per
    )
  #   log_message <- paste("stats:", nrow(statistics), "\n")
  # cat(log_message, file = "log.txt", append = TRUE)
    return(statistics)
  }
```





```{r}
#| include: false

# Function to process a single property and paddock dimension
process_property <- function(property_id, width_paddock, height_paddock) {
   #print("Starting process_property function") # Add this line
  # Your code for processing a single property and paddock dimension
  # Here you should use the provided property_id, width_paddock, and height_paddock
  # instead of the values from the loops.
  # 
  # print(paste(
  #   'id',
  #   property_id,
  #   'width_paddock',
  #   width_paddock,
  #   "Height",
  #   height_paddock
  # ))
  
  results_df <- data.frame()
    tryCatch({
      #print("Inside tryCatch block")


  property_id <- as.integer(property_id)
  # Select Property
  #print("Selecting property")
  property_boundary <- select_property(property_id)
  
  # Riparian Corridor check
  #print("Checking riparian corridor")
  riparian_corridor <- riparian_buffer(boundary_property = property_boundary,
           hydrology = hydro)
  

  # Property dimensions
 #print("Calculating property dimensions")
  pad_hedg_dim <- property_dimensions(
    desired_area = 600000,
    hedgerow_width = 100,
    width_paddock = width_paddock,
    height_paddock = height_paddock)
  
  # Create Grid , Rotate, Cut With Property
 #print("Creating grid, rotating, and cutting with property")
  property_grid <- grid_rotate(property_boundary, pad_hedg_dim)
  
  # Cut Grid w/ River
  #print("Cutting grid with river")
  property_fragment <- riparian_cut(riparian_corridor, property_grid)

  # Create Forest Reserve ≥ 25% 
  #print("Calculating forest reserve")
  forest_reserve <- reserve(property_fragment,property_boundary)
  
  # Property w/o reserve area
  # 
  #print("Calculating remaining area without forest reserve")
  property_remaining <- no_reserve_area(grid_property = property_fragment,
                  fr_union = forest_reserve)

  # Hedgerows
  #print("Dividing area into paddocks and hedgerows")
  hedgerows <- make_hedges(property_remaining)
  
  hedge <- st_erase(hedgerows, property_boundary)
  hedges <- st_difference(hedgerows, hedge)
  cut_reserve <- st_intersection(forest_reserve, hedges)
  hedges <- st_difference(hedges, cut_reserve) |> st_simplify(dTolerance = 10)
    
  #print("After processing hedgerows")
  
  # Paddocks
  paddocks <- make_paddocks(property_remaining, hedgerows)
 
  #print("After processing paddocks")
  # If there is a corridor cut edges
  if(is.null(riparian_corridor) == FALSE) {
  riparian_area <- sum(round(st_area(riparian_corridor),2))
  riparian_area_per <-
    sum((st_area(riparian_corridor)) / st_area(property_boundary)) * 100
     final_hedgerow <- st_difference(hedges, riparian_corridor) |> st_sf() |>
   st_collection_extract(type = 'POLYGON')
    
  } else{
    riparian_area <- NA
    riparian_area_per <- NA
    final_hedgerow <- hedges
  }
  
  
  
# print("Calculating final statistics")
#    log_message <- paste("Processing property_id:", property_id, "width_paddock:", width_paddock, "height_paddock:", height_paddock, "\n")
# cat(log_message, file = "log.txt", append = TRUE)
# print(log_message)

  
  # Final Areas
   statistics <-
     generate_statistics(
       property_boundary,
       width_paddock,
       height_paddock,
       forest_reserve,
       paddocks,
       final_hedgerow,
       riparian_area,
       riparian_area_per
     )
   # print('Check return of statistics')
   # print(paste("Number of rows in statistics:", nrow(statistics)))

  results_df <- bind_rows(results_df,statistics)

  #print("Done with process_property function")
  },
  
   error = function(e) {
     error_tibble <- tibble(
       cat = paste(property_id,width_paddock, height_paddock),
       error = as.character(e)
     )
   results_df <- bind_rows(results_df, error_tibble)
   })
  #print("After tryCatch block")
  #print(paste("Returning result for property_id:", property_id, ", width_paddock:", width_paddock, ", height_paddock:", height_paddock))
  #print(paste("Number of rows in statistics:", nrow(results_df$statistics)))
  # print(paste("Number of rows in results_df:", nrow(results_df)))
  

  return(results_df)
  }
  

```



# Function for purrr/furrr

```{r}
process_property_nested <- function(property_id, width_paddock, height_paddock) {
  result <- process_property(property_id, width_paddock, height_paddock)
  return(result)
}



```




# furrr
```{r}
#| include: false
#| warning: false
tic()
# Make sure to register the number of cores you want to use for parallel processing
plan(multisession, workers = 19)

# Create a list of property ids
property_ids <- unique(limit_lu$cat)

# Create paddock dimensions
paddock_dims <- create_paddock_dims()

# Run the process_property function for each property id and paddock dimension
results <- future_map_dfr(property_ids, function(property_id) {
  future_pmap_dfr(list(
    width_paddock = paddock_dims$width_paddock,
    height_paddock = paddock_dims$height_paddock
  ), function(width_paddock, height_paddock) {
    process_property_nested(property_id, width_paddock, height_paddock)
  })
})

# Combine the results
results_df <- bind_rows(results)
toc()
```



     
19 properties 1778.145 sec elapsed purrr
19 properties 209.476  sec elapsed furrr
5608properties 21535.431  sec elapsed furrr 
5608 properties 22472.561 sec elapsed furrr
797 properies 3209.14 sec elapsed


# RUN doParallel  & foreach (run  correct process_all_properties_parallel to switch)

```{r}
# Run the process for all properties and paddock dimensions in parallel
tic()
results <- process_all_properties_parallel(limit_lu, paddock_dims, n_cores)
toc()
```

# Example to workshop bugs
```{r}
# Call the function with some example data
example_width_paddock <- 1
example_height_paddock <- 1
```


```{r}
example_property_id <- limit_lu$cat[1]

```
# TEST doParallel  & foreach (run  correct process_all_properties_parallel to switch)


```{r}
property_results <- process_all_paddock_dims(example_property_id, paddock_dims)
```


```{r}
test_results <- process_property(example_property_id, example_width_paddock, example_height_paddock)
print(results)
```



# Test purrr
```{r}
test_result <- process_property(example_property_id, example_width_paddock, example_height_paddock)

```



 
 For after finding best ratio
 # Add your logic to store or return the results
  results_df <- list(
    property_boundary = property_boundary,
    riparian_corridor = riparian_corridor,
    pad_hedg_dim = pad_hedg_dim,
    property_grid = property_grid,
    property_fragment = property_fragment,
    forest_reserve = forest_reserve,
    property_remaining = property_remaining,
    hedgerows = hedgerows,
    paddocks = paddocks
  )

# Saving results to data folder
```{r}
#
# results_df5608 25%
# result_df5608_increase 50%
#saveRDS(results, '~/../../capstone/pyforest/data/results_5608/results5608_25.rds')
#saveRDS(results, '~/../../capstone/pyforest/data/results_5608/results5608_50.rds')

```

# Reload data 
```{r}
# load in results as running script again will overwrite results variable
results5608 <- readRDS("/Users/romero61/../../capstone/pyforest/data/results_5608/results5608_25.rds")

```

# REWORK TO DETERMINE Optimal ratios and paddocks sizes

```{r}
# Arrange the data by property_id, highest paddocks_area, and fr_area, and separate ratio_xy into width_paddock and height_paddock.
# Resulting dataset is optimal ratios 
optimal <- results5608 %>%
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)


# Optimal needs to be reworked into smaller paddocks subset properties with greater than 28% forest reserve

optimal_28 <- optimal |> 
  filter(fr_per >= 28) # on review this should have been just greater than but leaving for reproducibility

# subset limit_lu to properties that need to be reworked into smaller paddocks. First rework paddock area reduced to 990000 down from 999999
# 
#record of which properties to be reworked
rework_over28 <- limit_lu |> 
  filter(cat %in%  optimal_28$cat)

limit_lu <- rework_over28 #run 797 properties paddocks = 990000
```


```{r}
# save new reworked dataset
# 
#optimalrwk_result <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28.rds')
optimalrwk_result <- readRDS('~/../../capstone/pyforest/data/rework/results_rwk28.rds')
optimal_rwk <- optimalrwk_result %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup()  %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE) # 797 properties

# Second Subset 
optimal_28_2 <- optimal_rwk |> 
  filter(fr_per > 28)

#record of which properties to be reworked
rework_over28_2 <- limit_lu |> 
  filter(cat %in%  optimal_28_2$cat)

limit_lu <- rework_over28_2 #run 586 properties paddocks = 980000
```


```{r}
# save second new reworked dataset
# 
#optimalrwk_result2 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_2.rds')
optimalrwk_result2 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_2.rds')
optimal_rwk2 <- optimalrwk_result2 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE) # 596 properties

# Third Subset 
optimal_28_3 <- optimal_rwk2 |> 
  filter(fr_per > 28) |> 
  select(cat, fr_per, paddocks_area) |> 
  arrange( desc(fr_per))

theme_zebra(flextable(optimal_28_3))

#based on table using 970000 wont resolve issue so jumping to 950000
optimal_28_3 <- optimal_rwk2 |> 
  filter(fr_per > 28) 

#record of which properties to be reworked
rework_over28_3 <- limit_lu |> 
  filter(cat %in%  optimal_28_3$cat)

limit_lu <- rework_over28_3 # run 433 properties Paddocks =950000
```


```{r}
# save third new reworked dataset
# 
#optimalrwk_result3 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_3.rds')
optimalrwk_result3 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_3.rds')
optimal_rwk3 <- optimalrwk_result3 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)# 433 properties


# FOURTH Subset 
optimal_28_4 <- optimal_rwk3 |> 
  filter(fr_per > 28) |> 
  select(cat, fr_per, paddocks_area) |> 
  arrange( desc(fr_per))

theme_zebra(flextable(optimal_28_4)) # STILL AN ISSUE 



#Reset to rerun
optimal_28_4 <- optimal_rwk3 |> 
  filter(fr_per > 28) 

#record of which properties to be reworked
rework_over28_4 <- limit_lu |> 
  filter(cat %in%  optimal_28_4$cat)

limit_lu <- rework_over28_4 # run 208 properties Paddocks = 900000
```


```{r}
# save fourth new reworked dataset
# 
#optimalrwk_result4 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_4.rds')
optimalrwk_result4 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_4.rds')
optimal_rwk4 <- optimalrwk_result4 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)# 208 properties

# FIFTH Subset 
optimal_28_5 <- optimal_rwk4 |> 
  filter(fr_per > 28)

#record of which properties to be reworked
rework_over28_5 <- limit_lu |> 
  filter(cat %in%  optimal_28_5$cat)

limit_lu <- rework_over28_5 # run 76 properties Paddocks = 800000
```


```{r}
# save fifth new reworked dataset
# 
#optimalrwk_result5 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_5.rds')
optimalrwk_result5 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_5.rds')
optimal_rwk5 <- optimalrwk_result5 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)# 76 properties


# Sixth Subset 
optimal_28_6 <- optimal_rwk5 |> 
  filter(fr_per > 28)

#record of which properties to be reworked
rework_over28_6 <- limit_lu |> 
  filter(cat %in%  optimal_28_6$cat)

limit_lu <- rework_over28_6 # run 20 properties Paddocks = 700000
```


```{r}
# save sixth new reworked dataset
# 
#optimalrwk_result6 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_6.rds')
optimalrwk_result6 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_6.rds')
optimal_rwk6 <- optimalrwk_result6 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)# 20 properties

### STILL FOUR PROPERTIES OVER 28
### 1] 28.17 31.23 43.93 28.12
### 
### it'll likely take two more subsets
### or one big jump down


# Seventh Subset 
optimal_28_7 <- optimal_rwk6 |> 
  filter(fr_per > 28)

#record of which properties to be reworked
rework_over28_7 <- limit_lu |> 
  filter(cat %in%  optimal_28_7$cat)

limit_lu <- rework_over28_7 # run 4 properties Paddocks = 650000
```


```{r}
# save seventh new reworked dataset
# 
#optimalrwk_result7 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_7.rds')
optimalrwk_result7 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_7.rds')
optimal_rwk7 <- optimalrwk_result7 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)# 4 properties

# last Subset 
optimal_28_8 <- optimal_rwk7 |> 
  filter(fr_per > 28)

#record of which properties to be reworked
rework_over28_8 <- limit_lu |> 
  filter(cat %in%  optimal_28_8$cat)

limit_lu <- rework_over28_8 # run 1 properties Paddocks = 600000
```


```{r}
# save last new reworked dataset
# 
#optimalrwk_result8 <- results
#saveRDS(results, '~/../../capstone/pyforest/data/rework/results_rwk28_8.rds')
optimalrwk_result8 <- readRDS( '~/../../capstone/pyforest/data/rework/results_rwk28_8.rds')
optimal_rwk8 <- optimalrwk_result8 %>% 
  group_by(cat) %>%
  arrange(cat, desc(paddocks_area), desc(fr_area)) %>%
  slice(1) %>%
  ungroup() %>%
  separate(ratio_xy, into = c("width_paddock", "height_paddock"), sep = "/", convert = TRUE, remove = FALSE)# 4 properties
```

# OPTIMAL DIMENSIONS AND PADDOCKS

```{r}

# find reverse to gather less than 28 properties
optimal_28_r <- optimal |> 
  filter(fr_per < 28)  #important to use less than to not introduce duplicates from first initial error of using >= instead of just >.

optimal_28_2_r <- optimal_rwk |> 
  filter(fr_per <= 28)

optimal_28_3_r <- optimal_rwk2 |> 
  filter(fr_per <= 28) 

optimal_28_4_r <- optimal_rwk3 |> 
  filter(fr_per <= 28) 

optimal_28_5_r <- optimal_rwk4 |> 
  filter(fr_per <=28)

# Sixth Subset 
optimal_28_6_r <- optimal_rwk5 |> 
  filter(fr_per <= 28)

optimal_28_7_r <- optimal_rwk6 |> 
  filter(fr_per <= 28)

optimal_28_8_r <- optimal_rwk7 |> 
  filter(fr_per <= 28)

optimal_rwk8

# add in paddock size for those properties
optimal_28_r <- optimal_28_r %>% mutate(paddock_size = 999999)
optimal_28_2_r <- optimal_28_2_r %>% mutate(paddock_size = 990000)
optimal_28_3_r <- optimal_28_3_r %>% mutate(paddock_size = 980000)
optimal_28_4_r <- optimal_28_4_r %>% mutate(paddock_size = 950000)
optimal_28_5_r <- optimal_28_5_r %>% mutate(paddock_size = 900000)
optimal_28_6_r <- optimal_28_6_r %>% mutate(paddock_size = 800000)
optimal_28_7_r <- optimal_28_7_r %>% mutate(paddock_size = 700000)
optimal_28_8_r <- optimal_28_8_r %>% mutate(paddock_size = 650000)
optimal_rwk8 <- optimal_rwk8 %>% mutate(paddock_size = 600000)

optimal_xy <- bind_rows(optimal_28_r, optimal_28_2_r, optimal_28_3_r, optimal_28_4_r, optimal_28_5_r, optimal_28_6_r, optimal_28_7_r, optimal_28_8_r, optimal_rwk8)






# Finally, save the optimal xy for each property to create a lup with 25% forest reserve
# 
#saveRDS(optimal_xy, '/Users/romero61/../../capstone/pyforest/data/results_5608/optimal_xy_25.rds')
```

```{r}

# Reload Mock properties

limit_lu <- st_read('/Users/romero61/../../capstone/pyforest/data/mock_properties/mock_properties.shp')
# dataset to create map
# 
optimal_mock_properties <- limit_lu |> 
  left_join(optimal_xy %>%
              select(cat, width_paddock, height_paddock, paddock_size),
            by = "cat")
#save 
#
#st_write(optimal_mock_properties, '/Users/romero61/../../capstone/pyforest/data/optimal_mock_properties/optimal_mock_properties_25.gpkg')
```
# DEBUG DUPLICATES

```{r}
# Code if you find final optimal_xy has more rows than initial limit_lu


# # Create the optimal_xy dataframe with potential duplicates
# optimal_xy_with_duplicates <- bind_rows(optimal_28_r, optimal_28_2_r, optimal_28_3_r, optimal_28_4_r, optimal_28_5_r, optimal_28_6_r, optimal_28_7_r, optimal_28_8_r, optimal_rwk8)
# 
# cat_counts <- optimal_xy_with_duplicates %>%
#   count(cat) %>%
#   filter(n > 1)
# 
# cat_counts
# 
# duplicated_cat_rows <- optimal_xy_with_duplicates %>%
#   filter(cat %in% cat_counts$cat)
# 
# duplicated_cat_rows

# Remove duplicates by selecting the first row of each group based on 'cat'
# optimal_xy <- optimal_xy_with_duplicates %>%
#   group_by(cat) %>%
#   slice(1) %>%
#   ungroup()
# 
# optimal_xy
```

# PERCENTAGES
```{r}
percentages <- optimal_xy |>
  select(-riparian_area, -property_area, -property_units, -fr_area, -paddocks_area, -paddocks_units, - hedgerow_area, -fr_units) |>
  drop_units() |> 
  replace_na(replace = list(riparian_per = 0)) |> mutate(sum_percentage = fr_per + paddocks_per + hedgerow_per + riparian_per)
#saveRDS(statistics, "/Users/romero61/../../capstone/pyforest/data/results_df/statistics.rds")
theme_apa(flextable(percentages))
```

# purrr

```{r}
tic()
# Make sure to register the number of cores you want to use for parallel processing
# In this example, I am using 4 cores

# Create a list of property ids
property_ids <- unique(limit_lu$cat)

# Create paddock dimensions
paddock_dims <- create_paddock_dims()

# Run the process_property function for each property id and paddock dimension
results <- map_dfr(property_ids, function(property_id) {
  pmap_dfr(list(
    width_paddock = paddock_dims$width_paddock,
    height_paddock = paddock_dims$height_paddock
  ), function(width_paddock, height_paddock) {
    process_property_nested(property_id, width_paddock, height_paddock)
  })
})

# Combine the results
results_df <- bind_rows(results)
toc()
```

